Supplemental Information

### 2021-12-07 manuscript/supplement.Rmd
update manuscript with MYC data

---
title: "Supplemental Information"
subtitle: "Hypoxia uncouples HIF gene transcription and metabolic flux in proliferating primary cells"

@@

bibliography_main: library.bib
bibliography_software: packages.bib
csl: cell-metabolism.csl
link-citations: yes

output: 
  bookdown::word_document2:
    reference_docx: !expr system.file("manuscript", "template.docx", package = "Copeland.2021.hypoxia.flux")
    df_print: kable
    number_sections: false
    pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
      - '--lua-filter=pagebreak.lua'
      - '--lua-filter=multiple-bibliographies.lua'

compact-title: true
geometry: margin = 0.75in
fontsize: 11pt
mainfont: Calibri
graphics: yes

>>>>

---
title: "Supplemental Information"
subtitle: "MYC uncouples HIF target gene expression from glycolytic flux in hypoxic proliferating primary cells"

@@

bibliography_main: library.bib
bibliography_software: packages.bib
csl: cell-metabolism.csl
link-citations: yes
compact-title: true
geometry: margin = 0.75in
fontsize: 11pt
mainfont: Calibri
graphics: yes
